Analysis

### 2019-06-24 reports/DRM_exp/analysis_DRM_exp1.Rmd
fix error in perceptual distance

```{r SDT model plot}
df_dprime <- df %>% group_by(subject_id,type) %>% 
  summarize(correct = mean(correct),
            zH = qnorm(correct)) %>% 
  mutate(d_old_close = zH[type == "target"]-zH[type == "close distractor"],
         d_old_far = zH[type == "target"]-zH[type == "far distractor"],
         d_close_far = zH[type == "close distractor"]-zH[type == "far distractor"])

@@

p_SDT_model <- df_plot %>% ggplot(aes(x = x, y = y, col = type)) + geom_path(size = 1.2) + geom_vline(xintercept = 0) +
  theme(aspect.ratio = 1)
p_SDT_model
ggsave(file.path(plots_dir, "Fig_chp4_results_dprimedistance.eps"), p_dprimes, width = 6, height = 6)

>>>>

```{r SDT model plot}
df_dprime <- df %>% group_by(subject_id,type) %>%

  summarize(yes = mean(key_resp == "old"),
            zH = qnorm(yes)) %>% 
  mutate(d_old_close = zH[type == "target"]-zH[type == "close distractor"],
         d_old_far = zH[type == "target"]-zH[type == "far distractor"],
         d_close_far = zH[type == "close distractor"]-zH[type == "far distractor"])

@@

p_SDT_model <- df_plot %>% ggplot(aes(x = x, y = y, col = type)) + geom_path(size = 1.2) + geom_vline(xintercept = 0) +
  theme(aspect.ratio = 1)
p_SDT_model
ggsave(file.path(plots_dir, "Fig_chp4_results_dprimedistance.svg"), p_dprimes, width = 6, height = 6)
